### 2015-05-25 docs/report/code_sharing.tex
fixes code sharing subtitles

\subsubsection{\tstring{} serialization benchmarks}
One possible way of passing serialized \tfunction{}s to workers would be to encode them as binary and transfer them as an \tabuffer{}. To encode the strings there are two possible approaches:
\begin{itemize}
  \item Use the Encoding API\cite{encoding-api}
  \item Implement non native encoding/decoding functions
\end{itemize}

@@

\subsubsection{\tstring{} serialization and transfer benchmarks}
We created a benchmark using two functions whose string representation has different lengths to see if the function's length affected the serialization and transfer time. We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \tstring{} into an \tabuffer{}, sending it as a \code{Transferable} and decoding it on the Web Worker.
  \item Sending the string directly
  \item Using a \code{Blob} to store the stream and retrieving it in the Worker.
\end{enumerate}

>>>>

\subsubsection{\tstring{} encoding benchmarks}
One possible way of passing serialized \tfunction{}s to workers would be to encode them as binary and transfer them as an \tabuffer{}. To encode the strings there are two possible approaches:
\begin{itemize}
  \item Use the Encoding API\cite{encoding-api}
  \item Implement non native encoding/decoding functions
\end{itemize}

@@

\subsubsection{\tstring{} encoding and transfer benchmarks}
We created a benchmark using two functions whose string representation has different lengths to see if the function's length affected the serialization and transfer time. We measured three approaches to transfer the string:
\begin{enumerate}
  \item Encoding the \tstring{} into an \tabuffer{}, sending it as a \code{Transferable} and decoding it on the Web Worker.
  \item Sending the string directly
  \item Using a \code{Blob} to store the stream and retrieving it in the Worker.
\end{enumerate}
